---
title: "CWA Member Survey on Sexual Harassment - Open Ends"
author: "Anna Cooper, Office of the Secretary-Treasuer"
date: "July 31, 2018"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: false
---

<style type="text/css"> .table { margin-left:auto; margin-right:auto; width: 75%; } h1 { color: #B22222; font-size: 20px; } h2 { color: #ACB2BD; font-size: 15px; } h3 { color: #000000; font-size: 15px; } </style>

```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
options(knitr.kable.NA = '')
rm(list=ls())
library(aiHelper)
library(dplyr)
library(ggplot2)
require(survey)
require(Hmisc)
require(tidyr)
require(knitr)
require(magrittr)

# library(aiGraphs)
```

```{r read_in_data, echo = F, include = F}
# Read in data
setwd("C:/Users/acooper.CWA-UNION/Documents/Survey Research")

df <- read.csv('sh_july2018_weighted_final_v3_20180726.csv', header=T, na.strings = "")

dfh <- df[df$â..have.you.personally.experienced.any.of.the.following.harassments.at.your.current.job.or.workplace.within.the.last.year...verbal.harassment.of.a.sexual.nature..unwanted.touching.or.physical.contact..cyber.harassment..including.unwanted.comments.or.photos.shared.via.email..social.media..or.text...unwelcome.sexual.advances.or.requests.for.sexual.favors..physical.acts.of.sexual.assault..homophobic.or.transphobic.comments.or.behavior..sexism.or.gender.based.discrimination..other.forms.of.sexual.harassment.=="Yes",]


dfhome <- df[df$do.you.visit.homes.of.customers.or.clients.on.the.job.=="Yes" & !is.na(df$do.you.visit.homes.of.customers.or.clients.on.the.job.),]

#dfh <- read.csv('sh_hq_july2018_weighted_final.csv', header = T, na.strings = "")

#for age report
df$agerpt <- NA
df[df$raw_age < 35,]$agerpt <- "Less than 35"
df[df$raw_age >=35 & df$raw_age<45,]$agerpt <- "35 - 44"
df[df$raw_age >=45 & df$raw_age <55,]$agerpt <- "45 - 54"
df[df$raw_age >=55 & df$raw_age <65,]$agerpt <- "55 - 64"
df[df$raw_age >=65,]$agerpt <- "65+"
```

#Perpetrators

**Please answer whether within the last year people in any of the following roles have ever been perpetrators of sexual harassment against you at your current job.**

**Write-in responses for "Other".**

```{r echo = F}
perp <- table(df$other...write.in.please.answer.whether.within.the.last.year.people.in.any.of.the.following.roles.have.ever.been.perpetrators.of.sexual.harassment.against.you.at.your.current.job..check.all.that.apply..1)

knitr::kable(perp, col.names = c("Other perpetrators","Count"), align = c('l','r'))
```

#Reporting

**If you did not report to your union steward or representative, why not? Check all that apply.**

**Write-in responses for "Other".**

```{r echo = F}
stew<- table(df$other...write.in.if.you.did.not.report.to.your.union.steward.or.representative..why.not..check.all.that.apply..1)

knitr::kable(unique(df$other...write.in.if.you.did.not.report.to.your.union.steward.or.representative..why.not..check.all.that.apply..1), col.names = c("Other reasons sexual harassment was not reported to a a steward"), align = c('l'))
```

#Industry

**In which industry do you primarily work?**

**Write-in responses for "Other".**

```{r echo = F}
ind <- table(df$other...write.in.in.which.industry.do.you.primarily.work.)

knitr::kable(ind, col.names = c("Other industries","Count"), align = c('l','r'))
```

#Work location

**Please describe your work location.**

**Write-in responses for "Other".**

```{r echo = F}
loc <- table(df$other...write.in.please.describe.your.work.location.â..check.all.that.apply..1)

knitr::kable(loc, col.names = c("Other work locations","Count"), align = c('l','r'))
```

# Comments

**Additonal Comments**

```{r echo = F}

knitr::kable(unique(df[df$are.there.any.additional.comments.you.d.like.to.share.!="No" & df$are.there.any.additional.comments.you.d.like.to.share. !="None" &df$are.there.any.additional.comments.you.d.like.to.share.!="no" & df$are.there.any.additional.comments.you.d.like.to.share. != "Not at this time" & df$are.there.any.additional.comments.you.d.like.to.share. !="NONE" & df$are.there.any.additional.comments.you.d.like.to.share. != "none" & df$are.there.any.additional.comments.you.d.like.to.share. != "na" & df$are.there.any.additional.comments.you.d.like.to.share. != "Na" & df$are.there.any.additional.comments.you.d.like.to.share. != "N/A" & df$are.there.any.additional.comments.you.d.like.to.share. != "Nope" & df$are.there.any.additional.comments.you.d.like.to.share. != "N/a" & df$are.there.any.additional.comments.you.d.like.to.share. != "No", ]$are.there.any.additional.comments.you.d.like.to.share.), col.names = "Comments")
```